Securing Remote Access to Sensitive Data

### 2014-07-18 ccsw14/paper.tex
additions to introduction

One good example of a system for access to sensitive data is the data for the
United States Census.  The federal government established the Census Research
Data Centers to enable researchers access to unpublished Census data for the
purpose of conducting research that could provide guidance on public policy.

>>>>

One good example of a system for access to sensitive data is the data for the
United States Census.  The federal government established Census Research Data
Centers (RDCs) to enable researchers access to unpublished Census data for the
purpose of conducting research that could provide beneficial guidance to public
policy.  Once granted access, a researcher must visit one of the CRDCs in
person, and will then be permitted to use preallocated machines with preloaded
software in order to conduct their research.  Upon completion of their research,
their results are human-audited to protect confidentiality, and then released.
While this system provides access to Census data, and seems robust to data
leaks, it is also highly restrictive, requiring researchers to relocate and use
foreign hardware to conduct research.

More recently, the Centers for Medicare and Medicaid Services began providing
Medicare and Medicaid data using the CMS Virtual Research Data Center (VRDC) in
2013.  VRDC provides a more flexible model by allowing researchers to remotely
access desktop environments provided by a cloud infrastructure.  This model
relieves researchers of the need to travel to a physical location, and also
avoids the security risk of researchers having to receive and safeguard physical
copies of the data, while they are conducting their research.

However, even this remote access model is still restrictive, in that researchers
are largely limited to the data analysis tools and software that are made
available to them in their virtual environments, and any new data or software
one wishes to upload to a research environment must first undergo a review
process. To solve this substantial inconvenience, we propose a new system which
we call Data Capsules.  While, to an end user, a Data Capsules environment will
minimally differ from the type of environment provided by the CMS Virtual
Research Data Center, its design grants end users privileged access to install
software of their choice --- even down to the virtualization-compatible
operating system of their choice --- without requiring a review process and
without any compromise to the security of the data being provided.
